Abundance/diversity GAM

### 2021-04-14 code/ms1_abundance.Rmd
set up null model approach to preference analysis

# FL
gam_mean_fl_abund_01 <- gam(mean.fl.abund ~
                              management +
                              year +
                              s(bb.sp, bs = "re") +
                              s(elev.mean, by = bb.sp, k = 8),
                           method = "REML",
                           family = "tw",
                           select = TRUE,
                           data = abund_sum) %>% getViz()
```

### 2.2.3 Evaluate models
```{r}
# BB
check.gamViz(gam_max_bb_abund_01) # evaluate model
gam_max_bb_abund_01_sum <- summary(gam_max_bb_abund_01) # summarize model
print(plot(gam_max_bb_abund_01, allTerms = TRUE), pages = 1) # preliminary visualization

# FL
check.gamViz(gam_mean_fl_abund_01) # evaluate model
gam_mean_fl_abund_01_sum <- summary(gam_mean_fl_abund_01) # summarize model
print(plot(gam_mean_fl_abund_01, allTerms = TRUE), pages = 1) # preliminary visualization

>>>>

saveRDS(gam_max_bb_abund_01, "../output/gam_max_bb_abund_01.rds")

# FL
gam_mean_fl_abund_01 <- gam(mean.fl.abund ~
                              management +
                              year +
                              s(bb.sp, bs = "re") +
                              s(elev.mean, by = bb.sp, k = 8),
                           method = "REML",
                           family = "tw",
                           select = TRUE,
                           data = abund_sum) %>% getViz()

saveRDS(gam_mean_fl_abund_01, "../output/gam_mean_fl_abund_01.rds")
```

### 2.2.3 Evaluate models
```{r}
# BB
gam_max_bb_abund_01_check <- check.gamViz(gam_max_bb_abund_01) # evaluate model
gam_max_bb_abund_01_sum <- summary(gam_max_bb_abund_01) # summarize model
print(plot(gam_max_bb_abund_01, allTerms = TRUE), pages = 1) # preliminary visualization

# FL
gam_mean_fl_abund_01_check <- check.gamViz(gam_mean_fl_abund_01) # evaluate model
gam_mean_fl_abund_01_sum <- summary(gam_mean_fl_abund_01) # summarize model
print(plot(gam_mean_fl_abund_01, allTerms = TRUE), pages = 1) # preliminary visualization
